Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of TESS

### 2023-07-12 paper/ms.tex
update ms

% 250 word max!
\begin{abstract}
  Complex quasiperiodic variables (CQVs) are low-mass
  pre-main-sequence stars with nearly periodic optical modulation.
  The modulation is likely induced by dust or gas clumps in orbit at
  the Keplerian corotation radius.  Here, we report new CQVs
  discovered in TESS short-cadence data collected between July~2018 and Sep~2022.
  Our search of \nstarssearched\ K- and M-dwarfs with $T$$<$16 and
  $d$$<$150\,pc yielded \ngoods\ high-quality CQVs.  Most of these
  discoveries are new, and they include the brightest
  ($T$$\approx$9.5) and closest ($d$$\approx$20\,pc)
  examples of this class of object known, and perhaps the most massive
  ($\approx$0.6-0.8\,M$_\odot$).  A few objects are outliers among
  outliers; LP 12-502 for instance shows a ``dip complex'' with a
  period and total duration that are fixed over more than 1{,}000
  cycles, but which in detail exhibits anywhere from four to eight
  local minima per cycle.  LP-502 also displayed distinct superposed
  periods simultaneously, and showed drastic shape changes shortly
  after flares.  Broadly speaking, we find that none of the CQVs
  maintain a fixed light curve shape over timescales of more than a
  few hundred cycles, and we revisit the arguments for why transient
  corotating material is the most viable explanation.  In the future,
  we expect that our sample will facilitate modeling and observational
  efforts aimed at understanding these objects, and connecting them to
  the broader contexts of star, disk, and exoplanet evolution.
  For instance, if the transiting material is dust, then the rate of dip
  evolution implies that of order an asteroid belt's worth of mass
  passes through these structures over their lifetime of $10^8$ years.
\end{abstract}

@@

Table~\ref{tab:thetable} lists the \ncpvsfound\ objects identified by
our search.  \ngoods\ objects demonstrated what we viewed as
unambiguous characteristics of the CQV phenomenon in at least one TESS
sector; we refer to these as the ``high-quality sample''.  We found the
remaining \nmaybes\ CQV candidates to be ambiguous; their variability
might be caused by say, multiple starspot groups.  Additional data
from TESS or other instruments could help resolve their
classification.  The boolean \texttt{quality} column in the table divides
the two classes.  In the following discussion, we will restrict our
discussion to the high-quality sample.

The mosaic in Figure~\ref{fig:cqvs} shows phased light curves for the
\ngoods\ bonafide CQVs.  The objects are sorted first in order of the
number of TESS 120-second cadence sectors in which they clearly
demonstrated the CQV phenomenon, and secondarily by descending
brightness.  The objects at the top generally have the most 120-second
cadence data.  The top five objects by this metric are TIC~300651846
($T$$=$13.5, 12 sectors); TIC~402980664 ($T$$=$11.1, 7 sectors);
TIC~89463560 ($T$$=$13.5, 5 sectors); TIC~363963079 ($T$$=$12.9, 5
sectors); and TIC~294328887 ($T$$=$14.2, 4 sectors).  The brightest
five CQVs span 9.3$<$$T$$<$11.1; the faintest five span
14.5$<$$T$$<$15.0.  The fastest five have periods spanning
3.6\,hr$<$$P$$<$6.2\,hr, while the slowest five span
27\,hr$<$$P$$<$38\,hr.

@@

A small number of objects at first glance seem reminiscent of
eclipsing binaries, such as TIC~193831684 or TIC~5714469.  In these
few cases, we believe that that are unlikely to be eclipsing binaries
due to additional coherent variations in the light curves that are
distinct from any binary phenomenology of which we are aware.

@@

Of our \ncpvsfound\ confirmed and candidate CQVs, \nnotfieldbanyan\
were associated with a nearby moving group or open cluster using
BANYAN\,$\Sigma$.  The relevant groups are listed in
Table~\ref{tab:thetable}; their ages span $\approx$5-150\,Myr.  The
most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.  The yield
in Sco-Cen is not particularly surprising, since Sco-Cen contains the
majority of pre-main-sequence stars in the solar neighborhood.
However it is certainly likely given the $\lesssim$$10\%$ completeness
of TESS beyond 100\,pc that far more CQVs remains to be discovered in
Sco-Cen.  IC\,2602 and IC\,2391, which are located slightly beyond
100\,pc, are an example of this completeness effect: no CQVs appear in
those clusters from our search.

Of the \ngoodsfieldbanyan\ stars for which BANYAN\,$\Sigma$ did not
find any association, one (TIC~302160226) is a member of $\alpha$~Per
($t\approx 86\pm16$\,Myr;
\citealt{2021A&A...645A..84M,2023AJ....166...14B}).  For the other two
(TIC~58084670 and TIC~141146667), we were not able to confidently
associate either star with any young groups.  However both do seem to
clearly show the CQV signal over multiple TESS sectors, and both are
photometrically elevated relative to the main sequence.  For instance,
both were noted as being in the ``diffuse'' Class~III YSO population
near the Sun by \citet{2021ApJ...917...23K}.

Our catalog confirms that the CQV phenomenon persists for at least
$\approx$150\,Myr.  Our catalog includes three $\approx$150\,Myr CQVs
in AB~Dor \citep{2015MNRAS.454..593B}: TIC~288344202, TIC~332517282,
and TIC~368129164.  There is also a $\approx$112\,Myr old Pleiades CQV
(TIC~440725886; \citealt{2015ApJ...813..108D,CantatGaudin_2020}), and
a similarly-aged Psc-Eri member (TIC~38539720;
\citealt{2020A&A...639A..64R}).  To our best knowledge, TIC~332517282
was the previous record-holder for oldest-known CQV
\citep{2019ApJ...876..127Z,2022AJ....163..144G}; at least one
unambiguous case (EPIC~211070495) and a few other candidates were also
previously known in the Pleiades \citep{2016AJ....152..114R}.  While
we expect to have been sensitive to CQVs in the nearby Hyades
($\approx$700\,Myr), again due to the specifics of the TESS 120-second
selection function, we do not know at this time whether we would have
been sensitive to such stars.

Finally, six CQVs were identified in the recently confirmed Argus
association \citep{2019ApJ...870...27Z}.  This serves as an indirect
line of evidence supporting the reality, and youth, of that group.

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=\textwidth]{f6.pdf}
		\vspace{-0.45cm}
		\caption{
      {\bf Properties of CQVs identified by our search}.
      The \ngoods\ bonafide CQVs in Table~\ref{tab:thetable} are 
      the black circles; \nmaybes\ candidate CQVs are gray circles.
      The top panels show the \nstarssearched\ target stars with 120-second cadence data
      as the shaded gray background;
      darker regions correspond to a larger relative number of searched stars.
      {\bf lgb todo: P vs color needs Pleiades comparison}
		}
		\label{fig:catalogscatter}
	\end{center}
\end{figure*}

@@

Our observations provide a direct measurement of how often dips
appear and disappear, both due to sudden state-switches, and
due to more gradual, secular evolution.  For instance, LP~12-502
showed three ``state-switch'' events over the six months of available TESS
observations, during cycles 248-264, 299-315, and 1233-1247.  In each
case, a dip ``turned off''.  It is
plausible to imagine that these events correspond to either mass being
ejected from corotation, or perhaps being accreted onto the star.  In
either case, the corresponding $\dot{M} \equiv M\cdot {\rm d}N/{\rm d}t$
time-averaged over six months
is $\approx$3$\times$$10^{-18} M_\odot\,{\rm yr}^{-1} \approx
1\times10^{-12} M_\oplus\,{\rm yr}^{-1}$.  Considered cumulatively
over the $\approx$$10^8$ years for which the CQV phenomenon is
observed, this yields a cumulative moved dust mass of
$10^{-4}\,M_\oplus$, of order the Solar System's asteroid belt.
If the occulting material is gas, the masses involved would be of
order 100 times larger.
For cases in which we observe the {\it growth} of
dips, such as the Sector~29 data for TIC~224283342, the dip depths
typically increase by of order a few percent over ten to twenty days.
{\bf fixme: add closing sentence}

@@

\begin{enumerate}[leftmargin=*]
	%
  \item CQVs are {\it quasi}periodic.  While the mean periods in our
    sample remain fixed over the baseline of available
    observations, the light curve shapes always evolve over timescales
    of thousands of cycles (Figure~\ref{fig:evoln}).
  %
  \item The same CQV can show dips with similar but clearly
    distinct periods.  LP 12-502, for instance, showed dips with four
    distinct periods within $\pm 0.3\%$ of its fundamental period,
    sometimes simultaneously, and each lasting for up to 50 cycles
    (Figure~\ref{fig:lpriver0}).
  %
    \item CQVs evolve over timescales that are both secular
    ($>$100\,cycles) and impulsive ($<$1 cycle).  ``State-switches''
    can cause dips to collapse instantaneously, and are often (but not
    exclusively) linked with observed optical flares.  Dip growth
    however seems to happen over durations of at least ten cycles, and
    slow dip decay also happens.
  %
    \item The rate of dip evolution can be used to place a model-dependent
    constraint on amount of material that is either being accreted or ejected
    during the state changes (Section~\ref{subsec:massflux}).
    Order of magnitude estimates require at least an asteroid belt's worth
    of dust ($10^{-4}$\,$M_\oplus$) over $10^8$ years, or 100 times more 
    material if the occulting matter is gas.
  %
    \item The CQV phenomenon persists for $\gtrsim$150\,Myr, based on
    the existence of multiple CQVs in AB Dor, the Pleiades, and
    Psc-Eri (Section~\ref{subsec:starprops}).  It may extend to even
    older ages, however the lack of detected CQVs in the Hyades and
    Praesepe suggests that the lifetime of the phenomenon may be
    limited to the first few hundred million years.
	%
    \item The duty cycle for CQVs seems to be $\approx 75$\%, based on
    the fraction of bonafide CQVs that turned on or turned off during
    TESS re-observations, two years after their initial observation.
  %
    \item While the majority of detected CQVs have masses of
    0.1-0.5\,M$_\odot$, the upper mass limit for the CQV phenomenon
    might extend into the K-dwarf regime ($<$$0.8$\,M$_\odot$).
    TIC~405754448 and TIC~405910546, with masses of $\approx$0.8 and
    $\approx$0.6 solar masses, are the two massive outliers
    (Section~\ref{subsec:extreme}), and we encourage additional
    scrutiny of these objects in future work.
  %
    \item The closest CQVs to the Sun are at distances of 15-20\,pc, and
    the brightest CQVs have $V$$\approx$12 ($J$$\approx$7.5).  This
    conclusion is an extrapolation from the CQV sample derived in this work
    being $\gtrsim$80\% complete within 20\,pc.  Expanding our analysis of
    the TESS data to the full frame images would yield a truly
    volume-limited selection function, and would expand the CQV census
    by about a factor of two within 50\,pc, and by a factor of ten
    within 100\,pc.
\end{enumerate}

@@

\startlongtable
\begin{deluxetable}{rrrrrrlrllrrrr}
\tabletypesize{\footnotesize}
%\tabletypesize{\scriptsize}
\tablecaption{Complex quasiperiodic variables identified in the TESS 2-minute data. \label{tab:thetable}}
%\toprule
%TIC & $T$ & $d$ & BP-RP & RUWE & $P$ & assoc & age & teff & rstar & mstar & rcr & qual & Nsectors \\
%\midrule
%\endhead
\startdata
TIC & $T$ & $d$ & $\bprp$ & RUWE & $P$ & Assoc & Age & $T_{\rm eff}$ & $R_\star$ & $M_\star$ & $R$$_{\rm cr}$ & Quality & $N_{\rm sector}$ \\
-- & mag & pc & mag & -- & hr & -- & Myr & K & $R_\odot$ & $M_\odot$ & $R_\star$ & -- & -- \\
\hline
\input{20230613_LGB_RJ_CPV_TABLE_selfnapplied_rounded_data}
\enddata
\tablecomments{This table includes \ngoods\ CQVs (\texttt{Quality} flag true), and \nmaybes\ candidate CQVs (\texttt{Quality} flag false).  The machine-readable version, available online, includes additional columns for the Gaia DR2 source identifiers and parameter uncertainties.  The age uncertainties are typically $\approx \pm 10\%$,
	but can be asymmetric.  The median temperature, radius, and mass uncertainties are $\pm XXX$\,K, $\pm XX$\%, and $\pm YY$\% respectively.
	$N_{\rm sector}$ denotes the number of TESS sectors for which data are expected to be acquired between July~2018 and Oct~2024.   Association names and provenance follow conventions adopted by \citet{2018ApJ...856...23G}: 
	ABDMG: AB~Doradus moving group \citep{2015MNRAS.454..593B}.
	ARG: Argus \citep{2019ApJ...870...27Z}.
	APER: $\alpha$~Persei open cluster \citep{2023AJ....166...14B}.
	BPMG: $\beta$~Pic moving group \citep{2015MNRAS.454..593B}.
	CAR: Carina \citep{2015MNRAS.454..593B}.
	COL: Columba \citep{2015MNRAS.454..593B}.
	EPSC: $\epsilon$ Chamaeleontis \citep{2013MNRAS.435.1325M}.
	LCC: Lower Centaurus Crux \citep{2016MNRAS.461..794P}.
	PERI: Pisces-Eridani \citep{2019AJ....158...77C}.
	PLE: Pleiades \citep{2015ApJ...813..108D}.
	TAU: Taurus \citep{1995ApJS..101..117K}.
	THA: Tucana-Horologium assocation \citep{2015MNRAS.454..593B}.
	TWA: TW Hydrae assocation \citep{2015MNRAS.454..593B}.
	UCL: Upper Centaurus Lupus \citep{2016MNRAS.461..794P}.
	USCO: Upper Scorpius \citep{2016MNRAS.461..794P}.
}
\end{deluxetable}
\clearpage

>>>>

% 250 word max!
\begin{abstract}
  Complex quasiperiodic variables (CQVs) are low-mass
  pre-main-sequence stars with nearly periodic optical modulation.
  The modulation is likely induced by dust or gas clumps in orbit at
  the Keplerian corotation radius.  Here, we report new CQVs
  discovered in TESS short-cadence data collected between July~2018 and Sep~2022.
  Our search of \nstarssearched\ K- and M-dwarfs with $T$$<$16 and
  $d$$<$150\,pc yielded \ngoods\ high-quality CQVs.  Most of these
  discoveries are new, and they include the brightest
  ($T$$\approx$9.5) and closest ($d$$\approx$20\,pc)
  examples of this class of object known, and perhaps also the most massive
  ($\approx$0.6-0.8\,M$_\odot$).  A few objects are outliers among
  outliers; LP 12-502 for instance shows a ``dip complex'' with a
  period and total duration that are fixed over more than 1{,}000
  cycles, but which in detail exhibits anywhere from four to eight
  local minima per cycle.  LP-502 also displayed distinct superposed
  periods simultaneously, and showed drastic shape changes shortly
  after flares.  Broadly speaking, we find that none of the CQVs
  maintain a fixed light curve shape over timescales of more than a
  few hundred cycles, and we revisit the arguments for why transient
  corotating material is the most viable explanation.  In the future,
  we expect that our sample will facilitate modeling and observational
  efforts aimed at understanding these objects, and connecting them to
  the broader contexts of star, disk, and exoplanet evolution.
  For instance, if the transiting material is dust, then the rate of dip
  evolution implies that of order an asteroid belt's worth of mass
  passes through these structures over their lifetime of $\approx$$10^8$ years.
\end{abstract}

@@

Table~\ref{tab:thetable} lists the \ncpvsfound\ objects identified by
our search.  \ngoods\ objects demonstrated what we viewed as
unambiguous characteristics of the CQV phenomenon in at least one TESS
sector; we refer to these as the ``high-quality sample''.  The
classification of the remaining \nmaybes\ CQV candidates was ambiguous; their variability
might be caused by say, multiple starspot groups.  Additional data
from TESS or other instruments could help resolve their
classification.  The boolean \texttt{quality} column in the table divides
the two classes.  In the following discussion, we will restrict our
discussion to the high-quality sample.

The mosaic in Figure~\ref{fig:cqvs} shows phased light curves for the
\ngoods\ bonafide CQVs.  The objects are sorted first in order of the
number of TESS 120-second cadence sectors in which they clearly
demonstrated the CQV phenomenon, and secondarily by descending
brightness.  The objects at the top generally have the most 120-second
cadence data.  The top five objects by this metric are TIC~300651846
($T$$=$13.5, 12 sectors); TIC~402980664 ($T$$=$11.1, 7 sectors);
TIC~89463560 ($T$$=$13.5, 5 sectors); TIC~363963079 ($T$$=$12.9, 5
sectors); and TIC~294328887 ($T$$=$14.2, 4 sectors).  The brightest
five CQVs span 9.3$<$$T$$<$11.1; the faintest five span
14.5$<$$T$$<$15.0.  The fastest five have periods spanning
3.6\,hr$<$$P$$<$6.2\,hr, and the slowest five span
27\,hr$<$$P$$<$38\,hr.

@@

A small number of objects at first glance seem reminiscent of
eclipsing binaries, such as TIC~193831684 or TIC~5714469.  In these
few cases, we believe that that are unlikely to be eclipsing binaries
due to additional coherent variations in the light curves that are
distinct from any binary phenomenology of which we are aware.
Follow-up spectroscopy would be needed to definitively resolve this issue.

@@

Of our \ncpvsfound\ confirmed and candidate CQVs, \nnotfieldbanyan\
were associated with a nearby moving group or open cluster using
BANYAN\,$\Sigma$.  The relevant groups are listed in
Table~\ref{tab:thetable}; their ages span $\approx$5-200\,Myr.  The
most prodigious groups were Sco-Cen, Tuc-Hor, and Columba.  Six CQVs
were also identified in the Argus association
\citep{2019ApJ...870...27Z}, which serves as an indirect line of
evidence supporting the reality, and youth, of that group.  The yield
in Sco-Cen is not particularly surprising, since Sco-Cen contains the
majority of pre-main-sequence stars in the solar neighborhood.
However, given the $\lesssim$$10\%$ completeness
of TESS beyond 100\,pc, there are probably many more CQVs that remain to be discovered in
Sco-Cen.  IC\,2602 and IC\,2391, which are located slightly beyond
100\,pc, are an example of this completeness effect: our search did
not find any CQVs in those clusters.

Of the \ngoodsfieldbanyan\ stars for which BANYAN\,$\Sigma$ did not
find any association, one (TIC~302160226) is a member of $\alpha$~Per
($t\approx 86\pm16$\,Myr;
\citealt{2021A&A...645A..84M,2023AJ....166...14B}).  For the other two
(TIC~58084670 and TIC~141146667), we were not able to confidently
associate either star with any young groups.  However both do seem to
clearly show the CQV signal over multiple TESS sectors, and both are
photometrically elevated relative to the main sequence.  For instance,
both were noted by \citet{2021ApJ...917...23K} as being in the ``diffuse'' population
of $<$50\,Myr stars near the Sun.

Our search confirms that the CQV phenomenon persists for at least
$\approx$150\,Myr.  Table~\ref{tab:thetable} includes three $\approx$150\,Myr CQVs
in AB~Dor \citep{2015MNRAS.454..593B}, a $\approx$112\,Myr old Pleiades CQV
\citep{2015ApJ...813..108D}, and
a similarly-aged Psc-Eri member \citep{2020A&A...639A..64R}.  To our knowledge, TIC~332517282
in AB~Dor was the previous record-holder for oldest-known CQV
\citep{2019ApJ...876..127Z,2022AJ....163..144G}; at least one
unambiguous CQV (EPIC~211070495) and a few other candidates were also
previously known in the Pleiades \citep{2016AJ....152..114R}.

The upper age limit for the CQV phenomenon may even reach 200\,Myr,
based on the candidate membership of TIC~294328885 in the Carina Near
moving group \citep{2006ApJ...649L.115Z}.  This group's age primarily
rests on the lithium sequence of its G-dwarfs
\citep{2006ApJ...649L.115Z}, which shows a coeval population
of stars older than the Pleiades and younger than the 400\,Myr Ursa
Major moving group.  It would interesting to improve the
precision of the group's age measurement, for instance using
gyrochronology of F, G or K members, in order to verify this point.

%While
%we expect to have been sensitive to CQVs in the nearby Hyades
%($\approx$700\,Myr), again due to the specifics of the TESS 120-second
%selection function, we do not know at this time whether we would have
%been sensitive to such stars.

@@

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.9\textwidth]{f6.pdf}
		\vspace{-0.2cm}
		\caption{
      {\bf Properties of CQVs identified by our search}.
      The \ngoods\ bonafide CQVs in Table~\ref{tab:thetable} are 
      the dark blue circles; \nmaybes\ candidate CQVs are light blue circles.
      The top panels show the \nstarssearched\ target stars with 120-second cadence data
      as the shaded gray background;
      darker regions correspond to a larger relative number of searched stars.
      The lower-left panel compares the rotation--color distribution of the CQVs, and candidate CQVs, against the rotation
      periods of K- and M-dwarfs in the Pleiades from \citet{2016AJ....152..114R}.
      Note the scale change for the period $P$ from days to hours in the middle panel of the lower row.
		}
		\label{fig:catalogscatter}
	\end{center}
\end{figure*}

@@

Our observations provide a direct measurement of how often dips
appear and disappear, both due to sudden state-switches, and
due to more gradual, secular evolution.  For instance, LP~12-502
showed three ``state-switch'' events over the six months of available TESS
observations, during cycles 248-264, 299-315, and 1233-1247.  In each
case, a dip ``turned off''.  It is
plausible to imagine that these events correspond to either mass being
ejected from corotation, or perhaps being accreted onto the star.  In
either case, the corresponding $\dot{M} \equiv M\cdot {\rm d}N/{\rm d}t$
time-averaged over six months
is $\approx$3$\times$$10^{-18} M_\odot\,{\rm yr}^{-1} \approx
1\times10^{-12} M_\oplus\,{\rm yr}^{-1}$.  Considered cumulatively
over the $\approx$$10^8$ years for which the CQV phenomenon is
observed, this yields a cumulative moved dust mass of
$10^{-4}\,M_\oplus$, of order the Solar System's asteroid belt.
If the occulting material is gas, the masses involved would be of
order 100 times larger.
For cases in which we observe the {\it growth} of
dips, such as the Sector~29 data for TIC~224283342,
or Sector~5 of TIC~294328885,
the dip depths
typically increase by of order a few percent over ten to twenty days.
{\bf fixme: add closing sentence}

@@

\begin{enumerate}[leftmargin=*]
	%
  \item CQVs are quasiperiodic.  The mean periods 
    remain fixed over the $>$1{,}000-cycle baseline of available
    observations; but the light curve shapes always evolve (Figure~\ref{fig:evoln}).
  %
  \item The same CQV can show dips with similar but clearly
    distinct periods.  LP 12-502, for instance, showed dips with four
    distinct periods within $\pm 0.3\%$ of its fundamental period,
    sometimes simultaneously, and each lasting for up to 50 cycles
    (Figure~\ref{fig:lpriver0}).
  %
    \item CQVs evolve over timescales that are both secular
    ($>$100\,cycles) and impulsive ($<$1 cycle).  ``State-switches''
    can cause dips to collapse instantaneously, and are often (but not
    exclusively) linked with observed optical flares.  Dip growth
    however seems to happen over durations of at least ten cycles, and
    slow dip decay can also occur.
  %
    \item The rate of dip evolution can be used to place a model-dependent
    constraint on amount of material that is either being accreted or ejected
    during the state changes (Section~\ref{subsec:massflux}).
    Order of magnitude estimates require at least an asteroid belt's worth
    of dust ($10^{-4}$\,$M_\oplus$) over $10^8$ years, or 100 times more 
    material if the occulting matter is gas.
  %
  \item The CQV phenomenon persists for $\gtrsim$150\,Myr, based on
    the existence of multiple CQVs in AB Dor, the Pleiades, and
    Psc-Eri (Section~\ref{subsec:starprops}).  It may even extend to
    200\,Myr, based on the one CQV we found in the Carina Near
    moving group (TIC~294328885; $\approx$200\,Myr).  The lack of
    detected CQVs in the Hyades and Praesepe suggests that the
    lifetime of the phenomenon is likely limited to the first few
    hundred million years.
	%
    \item The duty cycle for CQVs seems to be $\approx 75$\%, based on
    the fraction of bonafide CQVs that turned on or turned off during
    TESS re-observations, two years after their initial observation.
  %
    \item While the majority of detected CQVs have masses of
    0.1-0.5\,M$_\odot$, the upper mass limit for the CQV phenomenon
    might extend into the K-dwarf regime ($<$$0.8$\,M$_\odot$).
    TIC~405754448 and TIC~405910546, with masses of $\approx$0.8 and
    $\approx$0.6 solar masses, are the two massive outliers
    (Section~\ref{subsec:extreme}), and we encourage additional
    scrutiny of these objects in future work.
  %
    \item The closest CQVs to the Sun are at distances of 15-20\,pc, and
    the brightest CQVs have $V$$\approx$12 ($J$$\approx$7.5).  This
    conclusion is an extrapolation from the CQV sample derived in this work
    being $\gtrsim$80\% complete within 20\,pc.  Expanding our analysis of
    the TESS data to the full frame images would yield a truly
    volume-limited selection function, and would expand the CQV census
    by about a factor of two within 50\,pc, and by a factor of ten
    within 100\,pc.
\end{enumerate}

@@

\startlongtable
\begin{deluxetable}{rrrrrrlrllrrrr}
\tabletypesize{\footnotesize}
%\tabletypesize{\scriptsize}
\tablecaption{Complex quasiperiodic variables identified in the TESS 2-minute data. \label{tab:thetable}}
%\toprule
%TIC & $T$ & $d$ & BP-RP & RUWE & $P$ & assoc & age & teff & rstar & mstar & rcr & qual & Nsectors \\
%\midrule
%\endhead
\startdata
TIC & $T$ & $d$ & $\bprp$ & RUWE & $P$ & Assoc & Age & $T_{\rm eff}$ & $R_\star$ & $M_\star$ & $R$$_{\rm cr}$ & Quality & $N_{\rm sector}$ \\
-- & mag & pc & mag & -- & hr & -- & Myr & K & $R_\odot$ & $M_\odot$ & $R_\star$ & -- & -- \\
\hline
\input{20230613_LGB_RJ_CPV_TABLE_selfnapplied_rounded_data}
\enddata
\tablecomments{This table includes \ngoods\ CQVs (\texttt{Quality} flag true), and \nmaybes\ candidate CQVs (\texttt{Quality} flag false).  The machine-readable version, available online, includes additional columns for the Gaia DR2 source identifiers and parameter uncertainties.  The age uncertainties are typically $\approx \pm 10\%$,
	but can be asymmetric.  The median temperature, radius, and mass uncertainties are $\pm XXX$\,K, $\pm XX$\%, and $\pm YY$\% respectively.
	$N_{\rm sector}$ denotes the number of TESS sectors for which data are expected to be acquired between July~2018 and Oct~2024.   Association names and provenance follow conventions adopted by \citet{2018ApJ...856...23G}: 
	ABDMG: AB~Doradus moving group \citep{2015MNRAS.454..593B}.
	ARG: Argus \citep{2019ApJ...870...27Z}.
	APER: $\alpha$~Persei open cluster \citep{2023AJ....166...14B}.
	BPMG: $\beta$~Pic moving group \citep{2015MNRAS.454..593B}.
  CARN: Carina Near moving group \citep{2006ApJ...649L.115Z}.
	COL: Columba \citep{2015MNRAS.454..593B}.
	EPSC: $\epsilon$ Chamaeleontis \citep{2013MNRAS.435.1325M}.
	LCC: Lower Centaurus Crux \citep{2016MNRAS.461..794P}.
	PERI: Pisces-Eridani \citep{2019AJ....158...77C}.
	PLE: Pleiades \citep{2015ApJ...813..108D}.
	TAU: Taurus \citep{1995ApJS..101..117K}.
	THA: Tucana-Horologium assocation \citep{2015MNRAS.454..593B}.
	TWA: TW Hydrae assocation \citep{2015MNRAS.454..593B}.
	UCL: Upper Centaurus Lupus \citep{2016MNRAS.461..794P}.
	USCO: Upper Scorpius \citep{2016MNRAS.461..794P}.
}
\end{deluxetable}
\clearpage
